Automated Formal Synthesis of Safe Digital Controllers\\ for Continuous Plants

### 2018-05-08 automatica/paper.tex
section 3

\title{Safe and Robust Formal Synthesis of Digital Controllers\\
for Continuous Plants}
% Title, preferably not more
% than 10 words.

@@

%% Using state of the art verifiers, we evaluate these models against
%% automatically synthesised controllers using CEGIS-based synsthesis that
%% incorporate the above mentioned artifacts in different models of
%% Single-Input/Single-Output (SISO) systems.
In this paper we present two novel approaches for the synthesis of
digital controllers, both of which make use of the framework known as CounterExample-Guided
Inductive Synthesis (CEGIS)~\cite{jha-icse10,
  DBLP:conf/asplos/Solar-LezamaTBSS06}, 
a technique from formal methods that has recently shown much promise and which we export in this work to a control-theoretical setup.  
CEGIS is an iterative process, where each iteration performs inductive
generalisation based on counterexamples provided by a verification
oracle \note{see Figure xxx}. The inductive generalisation uses information 
about a limited number of inputs to compute a candidate solution
for the entire range of possible inputs. Our two instantiations of CEGIS are described next.

@@

   \path
   ([yshift=2em]synth.east) edge node[align=center] {Candidate solution} ([yshift=2em]verif.west)
    ([yshift=-2em]verif.west) edge node[align=center] {Counterexample} ([yshift=-2em]synth.east)
    (verif) edge node {} (done);
 \end{tikzpicture}
}
 \caption{The CEGIS framework\label{fig:CEGIS}}
\end{figure*}

In this section, we give a brief description of the CEGIS framework~\cite{jha-icse10,
  DBLP:conf/asplos/Solar-LezamaTBSS06}, as illustrated in Figure~\ref{fig:CEGIS}.

We consider an input specification of the form $\exists P .\, \forall a.\, \phi(a, P)$, 
where $P$ ranges over functions (where a function is represented by the program computing it),
$a$ ranges over ground terms, 
and $\phi$ is a quantifier-free formula. 
We~interpret the ground terms over some domain~$\mathcal{D}$. 
This is a synthesis problem, where the objective is indeed to select a valid $P$ satisfying $\phi$ over all the $a$ terms.

CEGIS breaks down this generally hard synthesis problem into two easier parts:
%The design consists of two phases,
an inductive synthesis phase (denoted by {\sc Synthesize} in
Figure~\ref{fig:CEGIS}) and a validation phase (denoted by {\sc
  Verify}), which interact via a finite set of tests {\sc
  inputs} that is updated incrementally.
Given the specification $\phi$, the inductive synthesis procedure tries to
find an existential witness $P$ satisfying the specification
$\phi(a, P)$ for all $a$ in {\sc inputs} (as opposed to all $a \in
\mathcal{D}$).
%
If the synthesis phase succeeds in finding a witness~$P$, this witness is a
candidate solution to the full synthesis formula.  We pass this candidate
solution to the validation phase, which checks whether it is a full solution
(i.e., $P$ satisfies the specification $\phi(a, P)$ for all
$a\in\mathcal{D}$).  If this is the case, then the algorithm terminates. 
Otherwise, additional information is provided to the inductive synthesis
phase in the form of a new counterexample that is added to the {\sc inputs}
set and the loop iterates again.  %% More details about the general
%% architecture of the synthesizer can be found
%% in~\cite{DBLP:conf/lpar/DavidKL15}.
If the solution space is finite then the CEGIS loop is guaranteed to
terminate by either finding a solution or showing that no solution
exists.
%-------------------------------
\section{Formal specification of model properties} 
\label{sec:specification}
%-------------------------------

While in the previous section we discussed the generic CEGIS
framework, in the rest of the paper we will explain how we adapt it to
the synthesis of digital controllers. For this purpose, we start by
describing the specific property that we pass to the synthesizer as
the specification $\phi$. Namely, we are interested in capturing
stability and safety, which we discuss in Sections~\ref{ssec:stabspecification}
and~\ref{ssec:safespecification}, respectively.

>>>>

\title{Automated Formal Synthesis of Safe Digital Controllers\\
for Continuous Plants}
% Title, preferably not more
% than 10 words.

@@

%% Using state of the art verifiers, we evaluate these models against
%% automatically synthesised controllers using CEGIS-based synsthesis that
%% incorporate the above mentioned artifacts in different models of
%% Single-Input/Single-Output (SISO) systems.
In this paper we present two novel approaches for the synthesis of
digital controllers, both of which make use of the framework known as CounterExample-Guided
Inductive Synthesis (CEGIS)~\cite{jha-icse10,
  DBLP:conf/asplos/Solar-LezamaTBSS06}, 
  \note{we need to agree on how to spell out CEGIS}
a technique from formal methods that has recently shown much promise and which we export in this work to a control-theoretical setup.  
CEGIS is an iterative process, where each iteration performs inductive
generalisation based on counterexamples provided by a verification
oracle \note{see Figure xxx}. The inductive generalisation uses information 
about a limited number of inputs to compute a candidate solution
for the entire range of possible inputs. Our two instantiations of CEGIS are described next.

@@

   \path
   ([yshift=2em]synth.east) edge node[align=center] {Candidate solution} ([yshift=2em]verif.west)
    ([yshift=-2em]verif.west) edge node[align=center] {Counterexample} ([yshift=-2em]synth.east)
    (verif) edge node {} (done);
 \end{tikzpicture}
}
 \caption{The CEGIS framework\label{fig:CEGIS} \note{can we fit this figure within one column, and place it close to Sec 3.3?}}
\end{figure*}

In this section, we give a brief description of the CEGIS framework~\cite{jha-icse10,
  DBLP:conf/asplos/Solar-LezamaTBSS06}, which is illustrated in Figure~\ref{fig:CEGIS}. 
  CEGIS has been recently used for the automated synthesis of software programs, 
  and its setup is naturally that of mathematical logic.

We consider an input specification of the form $\exists P .\, \forall a.\, \phi(a, P)$, 
where $P$ ranges over functions (where a function is represented by the program computing it),
$a$ ranges over ground terms, 
and $\phi$ is a quantifier-free logical formula. 
We~interpret the ground terms over some domain~$\mathcal{D}$. 
This is a synthesis problem, where the objective is indeed to select a valid $P$ satisfying $\phi$ over all the $a$ terms.

CEGIS breaks down this generally hard synthesis problem into two easier parts:
%The design consists of two phases,
an inductive synthesis phase (denoted by {\sc Synthesize} in
Figure~\ref{fig:CEGIS}) and a validation phase (denoted by {\sc
  Verify}), which interact via a finite set of tests {\sc
  inputs} that is updated incrementally.
Given the specification $\phi$, the inductive synthesis procedure tries to
find an existential witness $P$ satisfying the specification
$\phi(a, P)$ for all $a$ in {\sc inputs} (as opposed to all $a \in
\mathcal{D}$).
%
If the synthesis phase succeeds in finding a witness~$P$, this witness is a
candidate solution to the full synthesis formula.  We pass this candidate
solution to the validation phase, which checks whether it is a full solution
(i.e., $P$ satisfies the specification $\phi(a, P)$ for all
$a\in\mathcal{D}$).  If this is the case, then the algorithm terminates. 
Otherwise, additional information is provided to the inductive synthesis
phase in the form of a new counterexample that is added to the {\sc inputs}
set and the loop iterates again.  %% More details about the general
%% architecture of the synthesizer can be found
%% in~\cite{DBLP:conf/lpar/DavidKL15}.
If the solution space is finite then the CEGIS loop is guaranteed to
terminate by either finding a solution or showing that no solution
exists.
%-------------------------------
\section{Formal specification of properties on a model} 
\label{sec:specification}
%-------------------------------

While in the previous section we have discussed the generic CEGIS
framework, in the rest of the paper we will explain how we adapt it to
the synthesis of digital controllers. For this purpose, we start by
describing the specific property that we pass to the synthesizer as
the specification $\phi$. Namely, we are interested in capturing
stability and safety, which we discuss in Sections~\ref{ssec:stabspecification}
and~\ref{ssec:safespecification}, respectively.
